---
title: "Homework 1"
author: Karina Myers
output: github_document
---

This is my solution to HW1. 

```{r}
library(tidyverse)
```

## Problem 1

create a data frame with the specified element. 

```{r}
prob1_df =
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0, 
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"), 
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
)
```

Take the mean of each variable in my data frame. 

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not the mean of character or factor. 

```{r, eval = FALSE} 
as.numeric(pull(prob1_df, samp_gt_0)) 
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

I can take take the mean of logical and factor, but not character. This happens because logical is converted to 0 or 1. Factor is converted to 1, 2, or 3. However, character is not converted to numbers, which is why you cannot take the mean. 


```{r, eval = FALSE} 
as.numeric(pull(prob1_df, samp_gt_0)) * (samp = rnorm(10))
as.factor(pull(prob1_df, samp_gt_0)) * (samp = rnorm(10))
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * (samp = rnorm(10))
```


## Problem 2 

```{r}
data("penguins", package = "palmerpenguins")

view(penguins)
variable.names(penguins)

summary(penguins$flipper_length_mm)

```

There are 334 penguin observations. Looking at penguin species, island, bill length, bill depth, flipper length, body mass, sex, and year. 

There are `r nrow(penguins)` rows and `r ncol(penguins)` columns. 

The mean flipper length is 200.9mm. 




```{r}
ggplot(prob2_df,
        x = bill_length_mm,
        y = flipper_length_mm)



set.seed(1)

plot_df = tibble(
  x = rnorm(1000, sd = .5),
  y = 1 + 2 * x + rnorm(1000)
)

ggplot(plot_df, aes(x = x)) + geom_histogram()

```






