---
title: "Homework 1"
author: Karina Myers
output: github_document
---

#### Loading tidyverse
```{r loading tidyverse}
library(tidyverse)
```

## Problem 1

#### Create a data frame with the specified elements
```{r}
prob1_df =
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0, 
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"), 
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
)
```

#### Take the Mean
```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not the mean of character or factor. 

#### Convert to Numeric
```{r, eval = FALSE} 
as.numeric(pull(prob1_df, samp_gt_0)) 
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

This shows how R coerces logical, character, and factor into numbers.
Logical is converted to 0 or 1. Factor is converted to 1, 2, or 3. 
However, character is not converted to numbers. This partially explains what happened in the step 
above. Since character could not be coerced to numbers, R could not take the mean. 

#### Second Code Chunk
```{r } 
#logical to numeric, and multiply the random sample by the result
as.numeric(pull(prob1_df, samp_gt_0)) * (samp = rnorm(10))
#logical vector to a factor, and multiply the random sample by the result
as.factor(pull(prob1_df, samp_gt_0)) * (samp = rnorm(10))
#logical vector to a factor then the result to numeric, and multiply the random sample by the result
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * (samp = rnorm(10))
```

## Problem 2 

#### Loading Penguins
```{r Loading Penguins}
data("penguins", package = "palmerpenguins")
```

The _penguins_ data set examines `r variable.names(penguins)`. 
This data set examines `r levels(penguins$species)` speices across three islands: `r levels(penguins$island)`. 
The mean bill length is `r mean(pull(penguins, bill_length_mm), na.rm = TRUE)`. Data was collected between the years of (`r range(pull(penguins, year), na.rm = TRUE)`). 
There are `r nrow(penguins)` rows and `r ncol(penguins)` columns. 
The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`. 

#### Scatterplot
```{r Scatterplot}
ggplot(data = penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + 
  geom_point() + 
  ggtitle("Flipper Length & Bill Length by Species")

ggsave("hw1_scatter_plot.pdf", height = 4, width = 6) 
```

